Codebook created on 2024-03-04 at 2024-03-04 10:16:26.447391

### 2024-03-06 Data/AnalysisData/codebook_Plot_46_data.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.
added (suggested) changes to methods section, and made the first appendix containing additional

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:47.216976"
output: github_document
---

@@

## Dataset description
The data contains 1925 cases and 4 variables.

>>>>

---
title: "Codebook created on 2024-03-04 at 2024-03-04 10:16:26.447391"
output: github_document
---

@@

## Dataset description
The data contains 2772 cases and 4 variables.
